Forest canopies are better generators of biodiversity in the tropics

### 2025-08-26 manuscript.Rmd
Update supplementary figure 1 and caption

```{r fig1, fig.id="fig1", fig.cap="a) Relationships between species richness and canopy height across all vertebrate taxa globally and in different biomes. Dots indicate observed values and lines indicate negative binomial model fits of richness as a function of canopy height (black) or richness as a function of the interaction between canopy height and biome. b-d) Spatial distribution of canopy height, vertebrate richness (for all vertebrates), and deviance residuals for the global model of vertebrate richness.", fig.height=100, fig.width=140}

@@

```{r splot-global-chrich, fig.id="global-chrich",  fig.lp="suppfig", fig.autonum.start_at=1, fig.cap="Global relationship between total vertebrate richness and canopy height. Line indicates predictions from a negative binomial model of richness by canopy height ± 95% CI. Points indicate observed richness by canopy height.", , fig.width=90, fig.height=90}

include_graphics("figures/ms_figures/supp_figs/total_richness~canopy.png", error = F)
```

```{r splot-resids-taxa, fig.id="resids-taxa", fig.lp="suppfig", fig.cap="Deviance residuals from negative binomial models of richness by canopy height for each vertebrate class: a) birds, b) mammals, c) reptiles, d) amphibians.", fig.width=180, fig.height=100}

include_graphics("figures/ms_figures/supp_figs/deviance_resids_taxa.png", error = F)
```

>>>>

```{r fig1, fig.id="fig1", fig.cap="a) Relationships between species richness and canopy height across all vertebrate taxa globally and in different biomes. Dots indicate observed values and lines indicate negative binomial model fits ± 95% CI of richness as a function of canopy height (black) or richness as a function of the interaction between canopy height and biome. b-d) Spatial distribution of canopy height, vertebrate richness (for all vertebrates), and deviance residuals for the global model of vertebrate richness.", fig.height=100, fig.width=140}

@@

```{r taxa-rich-ch, fig.id="taxa-rich-ch",  fig.lp="suppfig", fig.autonum.start_at=1, fig.cap=" a) Relationships between species richness and canopy height for birds, mammals, reptiles, and amphibians globally and in different biomes. Dots indicate observed values and lines indicate negative binomial model fits ± 95% CI of richness as a function of canopy height (black) or richness as a function of the interaction between canopy height and biome. b)  Deviance residuals from negative binomial models of global richness by canopy height for each vertebrate class.", fig.width=180, fig.height=200}

include_graphics("figures/ms_figures/supp_figs/richness~canopyHeight_taxa.png", error = F)
```
